The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-12-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added alternate paragraph about compareFPT

>>>>

\noindent \textcolor{red}{Another possibility:}

\textcolor{blue}{
   The general method applied calls upon functionality from the \emph{TestIdeals} package.
   The test ideals $\tau(f^t)$ of $f$ vary discretely with the parameter $t$; the function \texttt{FPureModule} in \emph{TestIdeals} is used  to compute the ``last'' test ideal of $f$ with parameter in the interval $[0,t)$.
   Comparing this with the test ideal $\tau(f^t)$, computed by the function \texttt{testIdeal}, we can determine whether $t$ is an $F$-jumping number of $f$, or more specifically, the $F$-pure threshold of $f$.
}
